DAG test

### 2022-11-14 DAG.Rmd
Commit

```{r}
tb_graph=sfcr_dag_cycles(eq)
```

>>>>

```{r, fig.width= 15, fig.height=10}
tb_graph=sfcr_dag_cycles(eq)

tb_graph

```{r, fig.width= 15, fig.height=10}
tb_graph %N>% 
  filter(!node_is_isolated()) %>%
  ggraph(layout = 'stress') + 
  geom_edge_fan(arrow = arrow(angle = 30, length = unit(0.25, 'cm'),type = 'closed'), alpha = 0.25) + 
  geom_node_point(aes(col = cyclical, size = centrality_eigen(directed = TRUE))) +
  geom_node_text(aes(label = name, size = centrality_eigen(directed = TRUE))) + 
  theme_graph() +
  theme(legend.position = "bottom") 
```

# 3d plot

```{r}

coords <- layout_with_fr(tb_graph, dim=3)
rglplot(tb_graph, layout=coords)
```
